---
title: "Codebook"
subtitle: "Public Sample"
output: 
  html_document: 
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_float: yes
    theme: flatly
date: "July 12th 2021"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knit_by_pkgdown <- !is.null(knitr::opts_chunk$get("fig.retina"))
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
library(codebook)
library(labelled)
library(ufs)
library(rio)
library(dplyr)
library(here)
```

# Description

This is the codebook of "Study 3" from the manuscript http://dx.doi.org/10.23668/psycharchives.3364 .  
Data is embeded in this file. To download the data as CSV `r xfun::embed_file(here("9_data+codebooks/rbt_study3_public.csv"), text ="click here")`.  
  
__Structure of the codebook:__
  
* Participants consecuatively received two abstracts (stimulus)
* They answered the scales in response to one abstract (stimulus) at a time
* The codebook reports each item and scale for the abstracts separately
* "abs1_" or "abs2_" in the scale name indicates if the item/scale refers to the first or second abstract

# Metadata



```{r import}
load(here("9_data+codebooks/rbt_study3_public.RData"))


# define several variables as character so they get plotted better
# rbt_public$position <- as.character(rbt_public$position)
rbt_public$country <- as.character(rbt_public$country)

rbt_public <- rbt_public %>%
  rename_at(vars(abs1_tsc_2, abs2_tsc_2),  add_R)

rbt_public <- rbt_public %>% 
    mutate_at(vars(matches("\\dR$")), reverse_labelled_values)

rbt_public <- rbt_public %>%
  dplyr::select(treat1:education)


rbt_public <- detect_scales(rbt_public, quiet = FALSE)
```

```{r metadata}
metadata(rbt_public)$name <- "Journals’ Open Science Badges Foster Trust in Scientists. Study 3: Public Sample."
metadata(rbt_public)$description <- "Code book to manuscript"
metadata(rbt_public)$identifier <- ""
metadata(rbt_public)$datePublished <- "2021-07-12"
metadata(rbt_public)$creator <- list(
      "@type" = "Person",
      givenName = "Schneider", familyName = "Jürgen",
      email = "juergen.schneider@uni-tuebingen.de", 
      affiliation = list("@type" = "Organization",
        name = "University of Tübingen"))
metadata(rbt_public)$citation <- "Schneider, J. (2021). Journals’ Open Science Badges Foster Trust in Scientists. Codebook of Study 3: Public sample"
```


```{r labels}
# add variable labels
var_label(rbt_public) <- list(
        treat1 = "First treatment condition, the participant was assigned to.",
        treat2 = "Second treatment condition, the participant was assigned to.",
        first_topic = "Topic the participant received first.",
        education = "Which is the highest qualifiaction you have?",
        abs1_tru_exp_1 = "competent - incompetent",
        abs1_tru_exp_2 = "intelligent - unintelligent",
        abs1_tru_exp_3 = "well educated -	poorly educated",
        abs1_tru_exp_4 = "professional - unprofessional",
        abs1_tru_exp_5 = "experienced - inexperienced",
        abs1_tru_exp_6 = "qualified - unqualified",
        abs1_tru_int_1 = "sincere - insincere",
        abs1_tru_int_2 = "honest - dishonest",
        abs1_tru_int_3 = "just - unjust",
        abs1_tru_int_4 = "fair - unfair",
        abs1_tru_ben_1 = "moral - immoral",
        abs1_tru_ben_2 = "ethical - unethical",
        abs1_tru_ben_3 = "responsible - irresponsible",
        abs1_tru_ben_4 = "considerate - inconsiderate",
        abs2_tru_exp_1 = "competent - incompetent",
        abs2_tru_exp_2 = "intelligent - unintelligent",
        abs2_tru_exp_3 = "well educated -	poorly educated",
        abs2_tru_exp_4 = "professional - unprofessional",
        abs2_tru_exp_5 = "experienced - inexperienced",
        abs2_tru_exp_6 = "qualified - unqualified",
        abs2_tru_int_1 = "sincere - insincere",
        abs2_tru_int_2 = "honest - dishonest",
        abs2_tru_int_3 = "just - unjust",
        abs2_tru_int_4 = "fair - unfair",
        abs2_tru_ben_1 = "moral - immoral",
        abs2_tru_ben_2 = "ethical - unethical",
        abs2_tru_ben_3 = "responsible - irresponsible",
        abs2_tru_ben_4 = "considerate - inconsiderate",
        country = "Country of residence",
        country_oth = "please specify other country"
)


# add value labels ##################################
val_labels(rbt_public$treat1) <- c("Greyed out badges (no adherence to Open Science standards)" = "gb",
                                "Control Condition (no badges)" = "cc",
                                "Colored out badges (adherence to Open Science standards)" = "cb")

val_labels(rbt_public$treat2) <- c("Greyed out badges (no adherence to Open Science standards)" = "gb",
                                "Control Condition (no badges)" = "cc",
                                "Colored out badges (adherence to Open Science standards)" = "cb")


# semantic differentials
add_semantic_diff <- function(x) {
  val_labels(x) <- c("1" = 1,
                     "2" = 2,
                     "3" = 3,
                     "4" = 4,
                     "5" = 5,
                     "6" = 6,
                     "7" = 7)
  x
}

rbt_public <- rbt_public %>%
  mutate_at(vars(abs1_tru_exp_1:abs1_tru_ben_4, abs2_tru_exp_1:abs2_tru_ben_4),  add_semantic_diff)

# education
val_labels(rbt_public$education) <- c("1 - 4 O levels / CSEs / GCSEs (any grades), ..." = "L12", # ...Entry Level, Foundation Diploma / NVQ Level 1, Foundation GNVQ, Basic Skills / 5+ O levels (passes) / CSEs (grade 1) / GCSEs (grades A*- C), School Certificate, 1 A level / 2 - 3 AS levels / VCEs, Higher Diploma / NVQ Level 2, Intermediate GNVQ, City and Guilds Craft, BTEC First / General Diploma, RSA Diploma, Baccalaureate Intermediate Diploma
                                      "2+ A levels / VCEs, 4+ AS levels, Higher School Certificate, ..." = "L34", # Progression / Advanced Diploma, Baccalaureate Advanced Diploma / NVQ Level 3, Advanced GNVQ, City and Guilds Advanced Craft, ONC, OND, BTEC National, RSA Advanced Diploma / Degree (for example BA, BSc), Higher degree (for example MA, PhD, PGCE) / NVQ Level 4 - 5, HNC, HND, RSA Higher Diploma, BTEC Higher Level, Foundation degree (NI) / Professional qualifications (for example teaching, nursing, accountancy)
                                      "Apprenticeship / Other vocational / work-related qualifications..." = "app") #  / Foreign qualifications / No academic or professional qualifications





# country
val_labels(rbt_public$country) <- c("United Kingdom" = "1",
                                 "Republic of Ireland" = "2",
                                 "USA" = "3",
                                 "Canada" = "4",
                                 "other" = "-999")
```


# Codebook

```{r codebook, echo=FALSE}
codebook(rbt_public, metadata_table = knit_by_pkgdown, metadata_json = TRUE)

if (!knit_by_pkgdown) {
  codebook:::escaped_table(codebook_table(rbt_public))
}
```

