---
title: "Codebook"
subtitle: "Undergraduates (pre-service teachers) Sample"
output: 
  html_document: 
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_float: yes
    theme: flatly
date: "July 12th 2021"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knit_by_pkgdown <- !is.null(knitr::opts_chunk$get("fig.retina"))
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
library(codebook)
library(labelled)
library(ufs)
library(rio)
library(dplyr)
library(here)
```

# Description

This is the codebook of "Study 1" from the manuscript http://dx.doi.org/10.23668/psycharchives.3364 .  
Data is embeded in this file. To download the data as CSV `r xfun::embed_file(here("9_data+codebooks/rbt_study1_undergrad.csv"), text ="click here")`.  
  
__Structure of the codebook:__
  
* Participants consecuatively received two abstracts (stimulus)
* They answered the scales in response to one abstract (stimulus) at a time
* The codebook reports each item and scale for the abstracts together (as in data set), therefore the reliability scores are not necessarily as reported in the manuscript
* for analyses that distinguish between the two measurement times, download the data and separate by variable `meas_rep`

# Metadata



```{r import}
rbt_ugr <- rio::import(here("9_data+codebooks/rbt_study1_undergrad.csv"))

# we need to invert items back to original format
inv7fct <- function(x) (8-as.numeric(x))

rbt_ugr <- rbt_ugr %>%
    mutate_at(vars(exp_1:exp_6, int_1:int_4, ben_1:ben_4),
              list(~inv7fct(.)))
```

```{r metadata}
metadata(rbt_ugr)$name <- "Journals’ Open Science Badges Foster Trust in Scientists. Study 1: Undergraduates Sample."
metadata(rbt_ugr)$description <- "Code book to manuscript"
metadata(rbt_ugr)$identifier <- ""
metadata(rbt_ugr)$datePublished <- "2021-07-12"
metadata(rbt_ugr)$creator <- list(
      "@type" = "Person",
      givenName = "Schneider", familyName = "Jürgen",
      email = "juergen.schneider@uni-tuebingen.de", 
      affiliation = list("@type" = "Organization",
        name = "University of Tübingen"))
metadata(rbt_ugr)$citation <- "Schneider, J. (2021). Journals’ Open Science Badges Foster Trust in Scientists. Codebook of Study 1: Undergraduates sample"
```


```{r labels}
# add variable labels #########################################################################
var_label(rbt_ugr) <- list(
        treat = "Treatment condition, the participant was assigned to.",
        exp_1 = "competent - incompetent",
        exp_2 = "intelligent - unintelligent",
        exp_3 = "well educated -	poorly educated",
        exp_4 = "professional - unprofessional",
        exp_5 = "experienced - inexperienced",
        exp_6 = "qualified - unqualified",
        int_1 = "sincere - insincere",
        int_2 = "honest - dishonest",
        int_3 = "just - unjust",
        int_4 = "fair - unfair",
        ben_1 = "moral - immoral",
        ben_2 = "ethical - unethical",
        ben_3 = "responsible - irresponsible",
        ben_4 = "considerate - inconsiderate",
        meas_rep = "Measurement repetition, first and second measurement",
        tsm_1 = "The insights from the text are arbitrary.",
        tsm_2 = "The knowledge contained in the text cannot be generalized to other situations at all.",
        tsm_3 = "The opposite of the knowledge formulated in the text would be equally right/wrong.",
        tsm_4 = "The knowledge formulated in the text cannot claim validity for other situations.",
        tch_1 = "It is transparent which data form the basis of the study.",
        tch_2 = "Interested parties can have a close look at the questionnaire of the described study.",
        tch_3 = "The data collected in the study are publicly available.",
        tch_4 = "The authors make it easy for other researchers to understand their statistical analyses.",
        tch_5 = "If other researchers want to repeat the study, they have easy access to the questionnaires used.",
        semester = "How many semesters of teaching/education-related coursework are you in (counting bachelor's degrees)?",
        sex = "Sex",
        age = "Age"
)


# add value labels ###########################################################################
# Treatment
val_labels(rbt_ugr$treat) <- c("Greyed out badges (no adherence to Open Science standards)" = "GB",
                               "Control Condition (no badges)" = "CC",
                               "Colored out badges (adherence to Open Science standards)" = "CB")

# add value labels (without "don't know" option) 
add_likert_labels4 <- function(x) {
  val_labels(x) <- c("fully disagree" = 1, 
                     "[empty 1]" = 2, 
                     "[empty 2]" = 3,
                     "fully agree" = 4)
  x
}

rbt_ugr <- rbt_ugr %>%
  mutate_at(vars(tsm_1:tsm_4),  add_likert_labels4)


# add value labels (with "don't know" option)
add_likert_labels4dk <- function(x) {
  val_labels(x) <- c("fully disagree" = 1, 
                     "[empty 1]" = 2, 
                     "[empty 2]" = 3,
                     "fully agree" = 4,
                     "don't know" = -999)
  x
}

rbt_ugr <- rbt_ugr %>%
  mutate_at(vars(tch_1:tch_5),  add_likert_labels4dk)


# semantic differentials
add_semantic_diff <- function(x) {
  val_labels(x) <- c("1" = 1,
                     "2" = 2,
                     "3" = 3,
                     "4" = 4,
                     "5" = 5,
                     "6" = 6,
                     "7" = 7)
  x
}

rbt_ugr <- rbt_ugr %>%
  mutate_at(vars(exp_1:exp_6, int_1:int_4, ben_1:ben_4),  add_semantic_diff)

# sex
val_labels(rbt_ugr$sex) <- c("female" = 1,
                             "male" = 2,
                             "other" = 3)

# measurement time
val_labels(rbt_ugr$meas_rep) <- c("first measurement" = 1,
                                  "second measurement" = 2)
 

# Define scales ##########################################################################
rbt_ugr$exp <- rbt_ugr %>% 
  select(exp_1:exp_6) %>% 
  aggregate_and_document_scale()

rbt_ugr$int <- rbt_ugr %>% 
  select(int_1:int_4) %>% 
  aggregate_and_document_scale()

rbt_ugr$ben <- rbt_ugr %>% 
  select(ben_1:ben_4) %>% 
  aggregate_and_document_scale()

rbt_ugr$tsm <- rbt_ugr %>% 
  select(tsm_1:tsm_4) %>% 
  aggregate_and_document_scale()

rbt_ugr$tch <- rbt_ugr %>% 
  select(tch_1:tch_5) %>% 
  aggregate_and_document_scale()


# detect scales #########################################################################
rbt_ugr <- detect_scales(rbt_ugr, quiet = FALSE)
```


# Codebook

```{r codebook, echo=FALSE}
codebook(rbt_ugr, metadata_table = knit_by_pkgdown, metadata_json = TRUE)

if (!knit_by_pkgdown) {
  codebook:::escaped_table(codebook_table(rbt_ugr))
}
```
