---
title: "Bayes Factor Design Analyses 'Re-Building Trust'"
author:
- "Jürgen Schneider"
- "Samuel Merk"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Design

We realize an intervention design with three conditions. Two if which will be randomly assigned to participants (within person design) - presenting all three would make variation too obvious and might create artifacts. As we assume $\mu 1$<$\mu 2$<$\mu 3$ with a small to medium effect ($d= .3-.4$), we computed power analyses for two t-tests with a power of $1-\beta = .90$ ($=.81$ for both tests). Below find power analyses with stopping rule at $BF= 10$ or $BF= \frac{1}{10}$ respectively and

* an effect of $d= .4$
* an effect of $d= .3$
* no effect ($d= 0$)

Out of financial and institutional reasons we aim for a $N_{max}= 250$. Due to expected variations in the BF with low $n$, we begin observing the data (optional stopping) at $n=150$.

# Power Analyses

## effect of $d= .4$

```{r , message = FALSE, warning = FALSE}
library(BFDA)

s1.4 <- BFDA.sim(expected.ES=0.4,
                 prior=list("Cauchy", list(prior.location=0, prior.scale=1)), 
                 n.min=20, stepsize=10, n.max=250, 
                 type="t.paired", 
                 design="sequential", 
                 alternative="greater", 
                 B=10000, 
                 cores=2, 
                 verbose=TRUE)

BFDA.analyze(s1.4, design="sequential", boundary=10)
plot(s1.4, n.min=150, boundary=c(1/10, 10))
                                               # As we plan to do 2 t-tests that supposed to have
SSD(s1.4, power=.90, boundary=c(1/10, 10))     # .8 power together, we aim for .90 power for each test.
```

## effect of $d= .3$

```{r , message = FALSE, warning = FALSE}

s1.3 <- BFDA.sim(expected.ES=0.3,
                 prior=list("Cauchy", list(prior.location=0, prior.scale=1)), 
                 n.min=20, stepsize=10, n.max=250, 
                 type="t.paired", 
                 design="sequential", 
                 alternative="greater", 
                 B=10000, 
                 cores=2, 
                 verbose=TRUE)


BFDA.analyze(s1.3, design="sequential", boundary=10)
plot(s1.3, n.min=150, boundary=c(1/10, 10))
SSD(s1.3, power=.90, boundary=c(1/10, 10))
```

## no effect ($d= 0$)

```{r , message = FALSE, warning = FALSE}
s0 <- BFDA.sim(expected.ES=0, 
               prior=list("Cauchy", list(prior.location=0, prior.scale=1)), 
               n.min=20, stepsize=10, n.max=250, 
               type="t.paired", 
               design="sequential", 
               alternative="greater", 
               B=10000, 
               cores=2, 
               verbose=TRUE)

BFDA.analyze(s0, design="sequential", boundary=1/10)
plot(s0, n.min=0, boundary=c(1/10, 10))
SSD(s0, alpha=.0025, boundary=c(1/10, 10))     # We aim for a .05 alpha, that is .0025 for 2 tests.
```

