---
title           : "(Re)Building Trust? Investigating the effects of open science badges on perceived trustworthiness of journal articles."
shorttitle      : "Preregistration (Re)Building Trust"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"

author: 
  - name        : "Jürgen Schneider"
    affiliation : 1
  - name        : "Samuel Merk"
    affiliation : 1
  - name        : "Tom Rosman"
    affiliation : 2
  - name        : "Augustin Kelava"
    affiliation : 1

affiliation:
  - id          : 1
    institution : "University of Tübingen"
  - id          : 2
    institution : "Leibniz Institute for Psychology Information"
bibliography: ../www/references.bib
output: prereg::cos_prereg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  dev = "cairo_pdf")
library(extrafont)
extrafont::loadfonts()
```

# Study Information

## Title
(Re)Building Trust. Investigating the effects of open science badges on perceived trustworthiness of journal articles.


## Description
The Replication Crisis diminishes trust in empirical sciences and with it the perceived value of science [@lupia.2018]. Open Science Practices (i.a. open data, open analysis script, open materials) are an increasingly popular approach to deal with challenges in replication and to rebuilt trust [@geukesetal.2016]. First investigations could, however, deliver no evidence toward the effect of Open Science Practices (OSP) on trustworthiness [@wingenetal.2019]. However, this study investigated the effect on a discipline level (psychology) with an abstract description of OSP. We want to shift the focus from discipline level to concrete individual journal articles and consider epistemic beliefs of readers to play a role [@merketal.2018]: Will visible OSP (vs. not visible vs. visibly non-OSP) foster perceived trustworthiness when reading journal articles of empirical studies? Hence we formulated the following research question:Will multiplistic epistemic beliefs moderate the relationship between OSP and trustworthiness?


## Hypotheses

1. Confirmatory, H1: Visible OSP (vs. not visible vs. visibly non-OSP) influence the perceived trustworthiness (subscale integrity). Our assumption: The more openness, the more trustworthy with small to moderate effects:  $\mu_1 < \mu_2 < \mu_3$. With the `bain` [@guetal.2019] package we will evaluate the following informative hypotheses using Bayes factors:  
   1. $\mu_1 < \mu_2 < \mu_3$
   2. $\mu_1 = \mu_2 = \mu_3$
   3. $\mu_1 < \mu_2 = \mu_3$
   4. $\mu_1 , \mu_2 , \mu_3$
2. Confirmatory, H2: The higher the topic specific multiplism, the lower the perceived trustworthiness (subscale integrity). Negative correlation.
3. Exploratory, H3: Topic specific multiplism moderates the effect of OSP on perceived trustworthiness (subscale integrity). 
4. Exploratory, H4: Visible OSP (vs. not visible vs. visibly non-OSP) have a negative effect on topic specific multiplism.


# Design Plan
<!-- In this section, you will be asked to describe the overall design of your study. Remember that this research plan is designed to register a single study, so if you have multiple experimental designs, please complete a separate preregistration. -->


## Study type
_Wording taken from OSF preregistration forms, since they are closed questions:_  

**Experiment**. A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.


## Blinding
<!-- Blinding describes who is aware of the experimental manipulations within a study. Select all that apply. Is there any additional blinding in this study? -->
_Wording taken from OSF preregistration forms, since they are closed questions:_  

* For studies that involve human subjects, they will not know the treatment group to which they have been assigned.
* Personnel who interact directly with the study subjects (either human or non-human subjects) will not be aware of the assigned treatments.


## Study design
<!-- Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.

This question has a variety of possible answers. The key is for a researcher to be as detailed as is necessary given the specifics of their design. Be careful to determine if every parameter has been specified in the description of the study design. There may be some overlap between this question and the following questions. That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information. For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information.

Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. -->

The design will include three conditions: visible Open Science Practices (visOSP), Practices not visible (nonvis) and visible non-Open Science Practices (nonOSP). Two of the (three) conditions are randomly chosen and randomized in their order within person. Realizing all three conditions within person would highlight the variation between conditions as too obvious and thus undermine blinding of subjects.  
visOSP condition: Subjects receive a title page of an empirical study (Title, Abstract, Keywords, Introduction, ...) together with three Open Science badges. The badges are explained using hints in style of speech bubbles and indicate that the authors engaged in the OSP open data, open analysis script and open materials.  
nonvis condition: Subjects receive a title page of an empirical study (Title, Abstract, Keywords, Introduction, ...) with no further information on Open Science, reflecting a "standard" journal article.
nonOSP condition: Subjects receive a title page of an empirical study (Title, Abstract, Keywords, Introduction, ...) together with three Open Science badges. The badges are explained using hints in style of speech bubbles and indicate that the authors did not engage in the OSP open data, open analysis script and open materials.  

As participants are exposed to more than one condition, we create all three conditions for three different empirical studies (topics). In doing so, we avoid participants to see one study topic twice under different conditions, which would undermine the blinding.


## Randomization
<!-- If you are doing a randomized study, how will you randomize, and at what level? Typical randomization techniques include: simple, block, stratified, and adaptive covariate randomization. If randomization is required for the study, the method should be specified here, not simply the source of random numbers.

Example: We will use block randomization, where each participant will be randomly assigned to one of the four equally sized, predetermined blocks. The random number list used to create these four blocks will be created using the web applications available at http://random.org. -->

* Randomization 1: Two of the three conditions will be randomly assigned to the participants.
* Randomization 2: The order of presentation will be randomized between the two conditions, within the participant.
* Randomization 3: Within each of the six combinations of randomization 1 & 2, we will randomize the order of the topic between (topic 1-2, 2-3, 3-1). 


# Sampling Plan
<!-- In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger data set, please describe the subset that will actually be used in your study. -->


## Existing data
<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io). -->
_Wording taken from OSF preregistration forms, since they are closed questions:_  
**Registration prior to analysis of the data**. As of the date of submission, the data exist and you have accessed it, though no analysis has been conducted related to the research plan (including calculation of summary statistics). A common situation for this scenario when a large data set exists that is used for many different studies over time, or when a data set is randomly split into a sample for exploratory analyses, and the other section of data is reserved for later confirmatory data analysis.



## Explanation of existing data
<!-- If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data. This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study.

An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the data set that had not been investigated by the researcher up to that point.

Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the data set that had not been investigated by the researcher up to that point. -->

We have already preregistered the study on [https://osf.io/2zypf](https://osf.io/2zypf) **prior to data collection**. There we planned two t-tests and hence used the according Bayes factor analysis. However, meanwhile we are aware of the capability of the framework used in the `bain` package - especially the opportunity to use multiply imputed data [@hoijtinketal.2019a]. We therefore created another preregistration.


## Data collection procedures
<!-- Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that don't include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.

The answer to this question requires a specific set of instructions so that another person could repeat the data collection procedures and recreate the study population. Alternatively, if the study population would be unable to be reproduced because it relies on a specific set of circumstances unlikely to be recreated (e.g., a community of people from a specific time and location), the criteria and methods for creating the group and the rationale for this unique set of subjects should be clear.

Example: Participants will be recruited through advertisements at local pastry shops. Participants will be paid $10 for agreeing to participate (raised to $30 if our sample size is not reached within 15 days of beginning recruitment). Participants must be at least 18 years old and be able to eat the ingredients of the pastries. -->

Our goal is to obtain a sample from the population of student teachers or teachers. This population is specifically suited to study the effect of Open Science Practices on trustworthiness, because it is part of their job to engage in evidence-based practice and thus stay up to date with research [@muntheetal.2015].

We plan to pass the data collection on to the Leibniz Institute for Psychology Information (ZPID).


## Sample size
<!-- Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis? For some studies, this will simply be the number of samples or the number of clusters. For others, this could be an expected range, minimum, or maximum number.

Example: Our target sample size is 280 participants. We will attempt to recruit up to 320, assuming that not all will complete the total task. -->

Our design analysis implies that for a $d=.3$ and a BF of $3$ or $\frac{1}{3}$ a sample of $N=250$ is sufficient.


## Sample size rationale
<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel. This gives you an opportunity to specifically state how the sample size will be determined. A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications. If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to "fill in the blanks." Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints.

Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. -->


**First preregistration:**  
Due to values missing by design, we approached data analysis and design analysis via two Bayes factor t-tests respectively. For design analysis we used the [`BFDA`](https://github.com/nicebread/BFDA) package.  
Required sample size from [first preregistration](https://osf.io/2zypf): For small to medium effect, stopping rule of Bayes Factor of $10$ ($\frac{1}{10}$ respectively) and 80% Power were N= 220. We thus aimed for a $N =250$ with optional stopping at $BF= 10$ or $\frac{1}{10}$ respectively. Due to expected variations in the BF with low $n$, we proposed to begin data observation at $n=150$.  
  
**Current Preregistration:**  
With the `bain` package we were able to tailor simulation to our design and specify informative hypotheses to be compared.  
We conducted design analysis for Bayesian repeated measures analysis (one within factor) with missing data.  
Based on the results of the first preregistration, we used $N =250$ as sample size for power analyses with informed hypothesis approach, too. The further settings were $d =.3$ and $BF= 3$ or $\frac{1}{3}$.

\scriptsize
```{r sampe size, code = readLines("design_analyses_simulation.R"), eval = F, out.width=12}
```

```{r plot design analysis, code = readLines("design_analyses_recodingplotting.R"), warning=F, message=F}
```
\normalsize

The results reveal good power under all hypotheses with the exception of $\mu_1 < \mu_2 = \mu_3$, where we find moderate power. Nevertheless, ...  
The results also reveal low probability of false-positive results with $N =250$, which justifies using a $BF= 3$ or $\frac{1}{3}$.

## Stopping rule
<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection. 

You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules. Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified. If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained.

Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week. We will post 20 new slots each week if, on that Friday night, we are below 320 participants. -->

Based on the Bayes factor design analysis we aim at $N =250$. A sample size slightly over $N =250$ might still be possible: We didn't implement automated stopping, but have to manually check the sample size and stop the online survey.



# Variables
<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so. -->



## Manipulated variables
<!-- Describe all variables you plan to manipulate and the levels or treatment arms of each variable. This is not applicable to any observational study. For any experimental manipulation, you should give a precise definition of each manipulated variable. This must include a precise description of the levels at which each variable will be set, or a specific definition for each categorical treatment. For example, “loud or quiet,” should instead give either a precise decibel level or a means of recreating each level. 'Presence/absence' or 'positive/negative' is an acceptable description if the variable is precisely described.

Example: We manipulated the percentage of sugar by mass added to brownies. The four levels of this categorical variable are: 15%, 20%, 25%, or 40% cane sugar by mass. -->
_Parallel to the [first preregistration](https://osf.io/2zypf):_  
There are three conditions:  

1. visOSP condition: Subjects receive a title page of an empirical study (Title, Abstract, Keywords, Introduction, ...) together with three Open Science badges. The badges are explained using hints in style of speech bubbles and indicate that the authors engaged in the OSP open data, open analysis script and open materials.
2. nonvis condition: Subjects receive a title page of an empirical study (Title, Abstract, Keywords, Introduction, ...) with no further information on Open Science, reflecting a "standard" journal article.
3. nonOSP condition: Subjects receive a title page of an empirical study (Title, Abstract, Keywords, Introduction, ...) together with three Open Science badges. The badges are explained using hints in style of speech bubbles and indicate that the authors did not engage in the OSP open data, open analysis script and open materials.  

See survey here: [https://osf.io/fh37z/](https://osf.io/fh37z/)


## Measured variables
<!-- Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.

Observational studies and meta-analyses will include only measured variables. As with the previous questions, the answers here must be precise. For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague. Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'

Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat. We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being 'not at all', 7 being 'a great deal') and 'How good did the brownie taste' (on a scale of 1-7, 1 being 'very bad', 7 being 'very good'). -->
_Parallel to the [first preregistration](https://osf.io/2zypf):_  

* Trustworthiness: We apply the Muenster Epistemic Trustworthiness Inventory [@hendriksetal.2015] with all three subscales. However as dependent variable we will only employ the subscale integrity. The other two subscales may be used for further exploratory analyses.  
* Topic-specific multiplism: We apply an established scale on the topic specific multiplism [@merketal.2017a].  
* Topic-specific consistency: We apply the stablished three item-measure [@merketal.2017a]  
* Treatment check (treatment-specific): We mesure the perceived openness/ transparency of the empirical study via specifically developed items.  
* Treatment check (global): We assess whether participants evaluate explanations of badges to be comprehensible, whether participants read the explanations and whether they perceive the explanations had an effect on their evaluations of authors.
* Additional small set of demographic variables will be assessed.  

For detailed insights, see survey here: [https://osf.io/fh37z/](https://osf.io/fh37z/)

## Indices
<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.

If you are using multiple pieces of data to construct a single variable, how will this occur? Both the data that are included and the formula or weights for each measure must be specified. Standard summary statistics, such as "means" do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined. For example, "biodiversity index" is too broad, whereas "Shannon’s biodiversity index" is appropriate.

Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->

We are going to built sum scores for the METI dimensions. Furthermore we will exploratory investigate the measurement invariance of the METI.


# Analysis Plan
<!-- You may describe one or more confirmatory analysis in this preregistration. Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.

A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis. You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required. -->


## Statistical models
<!-- What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions, subgroup analyses, pairwise or complex contrasts, or follow-up tests from omnibus tests. If you plan on using any positive controls, negative controls, or manipulation checks you may mention that here. Remember that any test not included here must be noted as an exploratory test in your final article.

This is perhaps the most important and most complicated question within the preregistration. As with all of the other questions, the key is to provide a specific recipe for analyzing the collected data. Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user? Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test. See the following examples:

- If someone specifies a 2x3 ANOVA with both factors within subjects, there is still flexibility with the various types of ANOVAs that could be run. Either a repeated measures ANOVA (RMANOVA) or a multivariate ANOVA (MANOVA) could be used for that design, which are two different tests. 
- If you are going to perform a sequential analysis and check after 50, 100, and 150 samples, you must also specify the p-values you’ll test against at those three points.

Example:  We will use a one-way between subjects ANOVA to analyze our results. The manipulated, categorical independent variable is 'sugar' whereas the dependent variable is our taste index. -->

Analyses will be conducted parallel to design analyses (see script above). If the data fails to meet assumptions, we plan to apply robust alternative analyses [@bosman.2018].


## Transformations
<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process. If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g. dummy coding, summation coding, etc.) and what the reference category will be.

Example: The "Effect of sugar on brownie tastiness" does not require any additional transformations. However, if it were using a regression analysis and each level of sweet had been categorically described (e.g. not sweet, somewhat sweet, sweet, and very sweet), 'sweet' could be dummy coded with 'not sweet' as the reference category. -->

None planned.


## Inference criteria
<!-- What criteria will you use to make inferences? Please describe the information you'll use (e.g. p-values, Bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

p-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields. Bayesian analyses should specify a Bayes factor or a credible interval. If you are selecting models, then how will you determine the relative quality of each? In regards to multiple comparisons, this is a question with few "wrong" answers. In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate. One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.

Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct. The post-hoc Tukey-Kramer test adjusts for multiple comparisons. -->

We will use Bayes factors with thresholds of $3$ (or $\frac{1}{3}$ respectively), based on the design analysis.


## Data exclusion
<!-- How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled? Will you use any awareness check? Any rule for excluding a particular set of data is acceptable. One may describe rules for excluding a participant or for identifying outlier data.

Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices. Outliers will be included in the analysis. -->

Implausible (consistent), out of theoretical range responses and participants taking less than 5 minutes for the survey may be eliminated for the analyses. The reasoning and decision to eliminate these participants will be made prior to data analysis and reported in disseminations.


## Missing data
<!-- How will you deal with incomplete or missing data? Any relevant explanation is acceptable. As a final reminder, remember that the final analysis must follow the specified plan, and deviations must be either strongly justified or included as a separate, exploratory analysis.

Example: If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis. -->
_Parallel to the [first preregistration](https://osf.io/2zypf):_  
Multiple imputation will be used.


## Exploratory analyses (optional)
<!-- If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.

Example: We expect that certain demographic traits may be related to taste preferences. Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences. -->
_Parallel to the [first preregistration](https://osf.io/2zypf):_  

* Hypothesis 3: BF Moderation Analysis will be conducted with visible OSP (vs. not visible vs. visibly non-OSP) as predictor, topic specific multiplism as moderator and perceived trust (subscale integrity) as dependent variable
* Hypothesis 4: BF analysis with visible OSP (vs. not visible vs. visibly non-OSP) as predictor and topic specific multiplism as dependent variable will be computed


# Other

## Other (Optional)
<!-- If there is any additional information that you feel needs to be included in your preregistration, please enter it here. Literature cited, disclosures of any related work such as replications or work that uses the same data, or other context that will be helpful for future readers would be appropriate here. -->




# References
## 
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
\noindent
